Delocalization of Eigenvectors in Random Matrices

### 2025-03-23 Draft.tex
open problem - multifractal partition functions

\noindent \textsc{I want to thank the friends that made this foreign land more hospitable:}\\
Jordan, the most gracious person I know, for being a strong positive influence in my life. \\
Tega, for always being there when things were most difficult. \\
John, for introducing me to powerlifting, which has become the bedrock I fall back on. \\
Jan, for bringing brotherly competition and pushing me to be better. \\
My blocking mates, Cameron and Leah, for all the late night conversations. \\
Kubra and Bolu, for making me feel seen and heard since day one on campus.
\vspace{0.25 cm}

@@

$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = p|W_{ij}|^{2p-2} \cdot \overline{W_{ij}} \cdot 1 \cdot (-G_{ik}G_{lj}) + p|W_{ij}|^{2p-2} \cdot W_{ij} \cdot 1 \cdot (-\overline{G_{ik}}\overline{G_{lj}})$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -p|W_{ij}|^{2p-2} \cdot [\overline{W_{ij}} \cdot G_{ik}G_{lj} + W_{ij} \cdot \overline{G_{ik}G_{lj}}]$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -p|W_{ij}|^{2p-2} \cdot [\overline{W_{ij}} \cdot G_{ik}G_{lj} + (\overline{W_{ij}} \cdot G_{ik}G_{lj})^*]$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -2p|W_{ij}|^{2p-2} \cdot \text{Re}(\overline{W_{ij}} \cdot G_{ik}G_{lj})$$
Hence, by putting everything together, we get:
$$\partial_{H_{k\ell}}F(H) = \partial_{H_{k\ell}} |W_{ij}|^{2p} = 2p|W_{ij}|^{2p-2}\text{Re}\left(W_{ij}\partial_{H_{k\ell}}\overline{W_{ij}}\right)= -2p|W_{ij}|^{2p-2}\text{Re}\left(W_{ij}\overline{G_{ik}G_{\ell j}}\right)$$
Let us calculate the second derivative is:

@@

As such, by combining the terms, we get the second derivative expansion: 
$$(8p^2-8p)|W_{ij}|^{2p-4}\text{Re}^2\left(W_{ij}\overline{G_{ik}G_{\ell j}}\right) +2p|W_{ij}|^{2p-2}\left(|G_{ik}G_{\ell j}|^2+\text{Re}\left(W_{ij}\overline{G_{ik}G_{kk}}\overline{G_{\ell j}}\right)+\text{Re}\left(\overline{G_{ik}}\overline{G_{\ell \ell}G_{\ell j}}\right)\right)$$

>>>>

\noindent \textsc{I want to thank the friends that made this foreign land more hospitable:}\\
Jordan, the most gracious person I know, for being a strong positive influence in my life. \\
Tega, for being there when things were most difficult. \\
Jan, for bringing brotherly competition and pushing me to be better. \\
John, for introducing me to powerlifting, which has become the bedrock I fall back on. \\
My blocking mates, Cameron and Leah, for all the late night conversations. \\
Kubra and Bolu, for making me feel seen and heard since day one on campus.
\vspace{0.25 cm}

@@

$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = p|W_{ij}|^{2p-2} \cdot \overline{W_{ij}} \cdot 1 \cdot (-G_{ik}G_{lj}) + p|W_{ij}|^{2p-2} \cdot W_{ij} \cdot 1 \cdot (-\overline{G_{ik}}\overline{G_{lj}})$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -p|W_{ij}|^{2p-2} \cdot [\overline{W_{ij}} \cdot G_{ik}G_{lj} + W_{ij} \cdot \overline{G_{ik}G_{lj}}]$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -p|W_{ij}|^{2p-2} \cdot [\overline{W_{ij}} \cdot G_{ik}G_{lj} + (\overline{W_{ij}} \cdot G_{ik}G_{lj})^*]$$
$$\frac{\partial |W_{ij}|^{2p}}{\partial H_{kl}} = -2p|W_{ij}|^{2p-2} \cdot \text{Re}(\overline{W_{ij}} \cdot G_{ik}G_{lj})$$
Hence, by putting everything together, we get:
$$\partial_{H_{k\ell}}F(H) = \partial_{H_{k\ell}} |W_{ij}|^{2p} = 2p|W_{ij}|^{2p-2}\text{Re}\left(W_{ij}\partial_{H_{k\ell}}\overline{W_{ij}}\right)= -2p|W_{ij}|^{2p-2}\text{Re}\left(W_{ij}\overline{G_{ik}G_{\ell j}}\right)$$
Let us calculate the second derivative:

@@

As such, by combining the terms, we get the following expansion: 
$$(8p^2-8p)|W_{ij}|^{2p-4}\text{Re}^2\left(W_{ij}\overline{G_{ik}G_{\ell j}}\right) +2p|W_{ij}|^{2p-2}\left[|G_{ik}G_{\ell j}|^2+\text{Re}\left(W_{ij}\overline{G_{ik}G_{kk}}\overline{G_{\ell j}}\right)+\text{Re}\left(\overline{G_{ik}}\overline{G_{\ell \ell}G_{\ell j}}\right)\right]$$
